### Options

```{r}
selectInput("par", "Parametric data", 
            choices = c("parametric", "nonparametric", "bayes", "robust"), 
            selected = "parametric", multiple = FALSE)

checkboxInput("getSummarizedData", "Calculate mean, sd, cv", value = TRUE)
checkboxInput("averageData", "Average data across condition", value = TRUE)
checkboxInput("diffData", "Calculate difference + means per participant", value = TRUE)
checkboxInput("heatmap", "Plot heatmap", value = FALSE)
numericInput("heatmap_bins", "Bins heatmaps", min = 0, max = Inf, value = 30, step = 1)

# Add selectors for x and y inputs for the correlation plot
selectizeInput("xVar", "X Variable for Correlation Plot", choices = muVars, selected = muVars[1], multiple = FALSE)
selectizeInput("yVar", "Y Variable for Correlation Plot", choices = muVars, selected = muVars[2], multiple = FALSE)
```

```{r}
checkboxInput("rm_clamped","Remove clamped offset values (for non-summarized data only)", value=TRUE)
```

Column
--------------------------------------------

### Correlation Plots  {data-height=500}
This page allows you to run some correlation tests on the selected data based on the settings on the left.

```{r}
# Add plot output for the correlation plot
imageOutput("correlation_plot")
```


### Correlation Results  {data-height=500}
```{r}
verbatimTextOutput("correlation_text")
```

### Homoscedasticity check
You should look for a consistent spread of residuals across the range of fitted values. If the data visually appear to have constant variance, a formal test like BP is often unnecessary.


```{r}
imageOutput("homoscedasticity_plot")
```

```{r, context="server"}
get_correlation_data <- reactive({
  if (input$getSummarizedData) {
    data <- get_mu_dyn_long()
    if (input$averageData) {
      data <- summarize_across_conditions(data)
    }
    if (input$diffData){
      data <- calculate_vfd_difference(data)
    }
  }
  else {
    data <- filteredParams()

    # Remove clamped data if the option is selected
    if (input$rm_clamped) {
    data <- data %>%
      filter(!(heelStrikes.offset_x == 0.075 | heelStrikes.offset_x == -0.075 | heelStrikes.offset_z == 0.15 | heelStrikes.offset_z == -0.15))
    }
  }

  return(data)
})

get_selected_value <- function(current_value, prev_choices, new_choices) {
  # Check if previous choices exist and if the current value is in the previous choices
  if (!is.null(prev_choices) && current_value %in% prev_choices) {
    # Find the index of the currently selected variable in the previous choices
    index <- match(current_value, prev_choices)
    # Try to select the same index in the new choices, if it exists
    if (index <= length(new_choices)) {
      return(new_choices[index])
    } else {
      # Fallback to the first item if index is out of bounds
      return(new_choices[1])
    }
  } else {
    # Fallback to the first item if previous choices don't exist or current value is not in them
    return(new_choices[1])
  }
}

# Store previous numeric columns as a reactive value
previous_numeric_cols <- reactiveVal()

# Update the selectizeInput choices based on the filtered data for correlation plot
observe({
  # Get the latest data and numeric columns
  data <- get_correlation_data()
  numeric_cols <- names(data)[sapply(data, is.numeric)]
  
  # Retrieve previous numeric columns and update the stored value
  prev_numeric_cols <- previous_numeric_cols()
  
  # Only proceed if numeric_cols have actually changed to avoid unnecessary updates
  if (!identical(numeric_cols, prev_numeric_cols)) {
    previous_numeric_cols(numeric_cols)  # Update reactive value to the current numeric_cols
    
    # Use isolate to prevent reactive dependencies within selected variables
    s_xVar <- isolate(input$xVar)
    s_yVar <- isolate(input$yVar)
    
    # Use the function to get selected values based on previous choices' positions
    selected_xVar <- get_selected_value(s_xVar, prev_numeric_cols, numeric_cols)
    selected_yVar <- get_selected_value(s_yVar, prev_numeric_cols, numeric_cols)
    
    # Update the selectize inputs only if there has been a change in choices
    updateSelectizeInput(session, "xVar", choices = numeric_cols, selected = selected_xVar)
    updateSelectizeInput(session, "yVar", choices = numeric_cols, selected = selected_yVar)
  }
})
  
output$correlation_text <- renderPrint({
  dt <- get_correlation_data()
  
  cat("---CHECKING PARAMETRIC ASSUMPTIONS---\n")
  # Check normality of the selected variables
  cat("Number of datapoints: ", length(dt[[input$xVar]]))
  shapiro_x <- shapiro.test(dt[[input$xVar]])
  shapiro_y <- shapiro.test(dt[[input$yVar]])
  print(shapiro_x)
  print(shapiro_y)
  
    # Check homoscedasticity: Breusch-Pagan test
  model <- lm(dt[[input$yVar]] ~ dt[[input$xVar]])
  bp_test <- bptest(model)
  cat("Breusch-Pagan Test for Homoscedasticity:\n")
  print(bp_test)

  # Interpretation of homoscedasticity
  if (bp_test$p.value > 0.05) {
    cat("Interpretation: The p-value is", bp_test$p.value, 
        "> 0.05, so we assume homoscedasticity.\n")
  } else {
    cat("Interpretation: The p-value is", bp_test$p.value, 
        "< 0.05, indicating that the homoscedasticity assumption is violated.\n")
  }
  
  cat("Also check plot:\n")
  cat("  - The x-axis represents the fitted values, and the y-axis represents the residuals.\n  - Ideally, the residuals should be randomly scattered around the horizontal line at 0, without any clear pattern, indicating homoscedasticity.\n")
  
  # Determine correlation method based on input
  cat("---CORRELATION RESULTS---\n\n")
  method <- switch(input$par,
                   parametric = "pearson",
                   nonparametric = "spearman",
                   bayes = "bayes",
                   robust = "robust")
  print(paste("Using method:",method))
  # Calculate correlation
  if (method == "bayes") {
    correlation <- correlationBF(dt[[input$xVar]], dt[[input$yVar]])
    result_text <- paste("Bayesian correlation between", input$xVar, "and", input$yVar, ":", correlation)
    cat(result_text, "\n")
  } else if (method == "robust") {
    correlation <- pbcor(dt[[input$xVar]], dt[[input$yVar]])
    result_text <- paste("Robust correlation between", input$xVar, "and", input$yVar, ":", correlation)
    cat(result_text, "\n")
  } else {
    correlation <- cor.test(dt[[input$xVar]], dt[[input$yVar]], method = method)
    result_text <- paste("Correlation between", input$xVar, "and", input$yVar, ":",
                         correlation$estimate, "\n",
                         "p-value:", correlation$p.value, "\n",
                         "Confidence interval:", correlation$conf.int[1], "-", correlation$conf.int[2])
    cat(result_text, "\n")
    
    # Additional information
    if (abs(correlation$estimate) > 0.7) {
      strength <- "strong"
    } else if (abs(correlation$estimate) > 0.5) {
      strength <- "moderate"
    } else {
      strength <- "weak"
    }
    
    cat("The correlation is", strength, "\n")
    
    if (correlation$p.value < 0.05) {
      cat("The correlation is statistically significant.\n")
    } else {
      cat("The correlation is not statistically significant.\n")
    }
  }
})

output$homoscedasticity_plot <- renderSVG({ reactive({
  dt <- get_correlation_data()
  
  # Fit a linear model
  model <- lm(dt[[input$yVar]] ~ dt[[input$xVar]])
  
  # Get fitted values and residuals
  fitted_vals <- fitted(model)
  residuals <- resid(model)
  
  # Plot residuals vs. fitted values
  plot(fitted_vals, residuals,
       main = "Residuals vs Fitted Values",
       xlab = "Fitted Values",
       ylab = "Residuals",
       pch = 19, col = "darkgrey")
  
  # Add a horizontal line at 0
  abline(h = 0, col = "red", lwd = 2)
  
  # Add Loess smoothing line to check for any pattern in residuals
  lines(lowess(fitted_vals, residuals), col = "blue", lwd = 2)
}) })


output$correlation_plot <- renderSVG({ reactive({
  dt <- get_correlation_data()
  
  # Ensure the selected variables exist in the dataset
  if (input$xVar %in% names(dt) && input$yVar %in% names(dt)) {
    x_var <- sym(input$xVar)
    y_var <- sym(input$yVar)
    
    #ggscatterstats(data = dt, x = !!x_var, y = !!y_var, type = input$par) + theme_minimal(base_size = input$baseSize)
    plot_correlation_stats(dt, input$xVar, input$yVar, input$par, input$baseSize, input$heatmap, input$heatmap_bins)
  } else {
    # Print a message if the variables are not found
    plot.new()
    text(0.5, 0.5, "Selected variables not found in the dataset", cex = 1.5, col = "red")
  }
}) 
})
```