---
title: "Participant Report for: `r params$participant`"
output: pdf_document
params:
  participant: NA
  traj_plots_z: NA
  traj_plots_y: NA
  traj_plots_x: NA
  pie_charts: NA
  questionnaire_plots: NA
  variability_plots: NA
  scatter_plot: NA
  disturbance_plots_z_l: NA
  disturbance_plots_x_l: NA
  disturbance_plots_z_r: NA
  disturbance_plots_x_r: NA
  eye_plots_x: NA
  eye_plots_z: NA
---

```{r setup, include=FALSE}
library(gridExtra)
library(grid)

# Access parameters
participant <- params$participant
traj_plots_z <- params$traj_plots_z
traj_plots_y <- params$traj_plots_y
traj_plots_x <- params$traj_plots_x
pie_charts <- params$pie_charts
questionnaire_plots <- params$questionnaire_plots
variability_plots <- params$variability_plots
scatter_plot <- params$scatter_plot
disturbance_plots_z_l <- params$disturbance_plots_z_l
disturbance_plots_x_l <- params$disturbance_plots_x_l
disturbance_plots_z_r <- params$disturbance_plots_z_r
disturbance_plots_x_r <- params$disturbance_plots_x_r
eye_plots_x <- params$eye_plots_x
eye_plots_z <- params$eye_plots_z
```

### Page 1: Variability Plots, Scatter Plot, Target Stepping Plot
```{r, fig.width = 8.3, fig.height = 9}
# Combine variability plots with scatter plot and target stepping plot
all_plots <- scatter_plot

# Arrange Variability Plots, Scatter Plot, and Target Stepping Plot
grid.arrange(
  grobs = list(
    arrangeGrob(grobs = all_plots, ncol = 2, widths = c(1.5,1)),
    arrangeGrob(grobs = variability_plots, ncol = 3)
  ),
  ncol = 1, heights = c(1,1)
)
```

### Page 2: Questionnaire Results
```{r, fig.width = 8.3, fig.height = 11.7}
# Arrange Questionnaire Results
grid.arrange(
  grobs = questionnaire_plots,
  ncol = 1,
  heights = c(1, 1, 1)  # Adjust height ratios if needed
)
```

### Page 3: Right-Left - x pos - Foot Trajectories

```{r, fig.width = 8.3, fig.height = 11.7}
# Ensure that all elements are grobs
#foot_trajectories <- lapply(1:length(traj_plots_z), function(i) {
#  list(ggplotGrob(traj_plots_z[[i]]), ggplotGrob(traj_plots_y[[i]]), ggplotGrob(traj_plots_x[[i]]))
#})
# Flatten the list of lists into a single list
#foot_trajectories <- do.call(c, foot_trajectories)

# Arrange Foot Trajectories and Pie Charts
grid.arrange(
  grobs = list(
    arrangeGrob(grobs = traj_plots_x, ncol = 1)
  ), ncol = 1
)
```

### Page 4: Front-Back - z pos - Foot Trajectories

```{r, fig.width = 8.3, fig.height = 11.7}
# Arrange Foot Trajectories and Pie Charts
grid.arrange(
  grobs = list(
    arrangeGrob(grobs = traj_plots_z, ncol = 1))
)
```

### Page 5: Up-Down - y pos - Foot Trajectories

```{r, fig.width = 8.3, fig.height = 11.7}
# Arrange Foot Trajectories and Pie Charts
grid.arrange(
  grobs = list(
    arrangeGrob(grobs = traj_plots_y, ncol = 1))
)
```

### Page 6: Pie-Charts

```{r, fig.width = 8.3, fig.height = 11.7}
# Arrange Foot Trajectories and Pie Charts
grid.arrange(
  grobs = list(
    arrangeGrob(grobs = lapply(pie_charts, ggplotGrob), ncol = 2, heights = c(1, 1))
    )
)
```


### Page 7: Eye - hit pos x

```{r, fig.width = 8.3, fig.height = 11.7}
# Arrange Eye Plots - hit pos x
grid.arrange(
  grobs = list(
    arrangeGrob(grobs = eye_plots_x, ncol = 1)
  ), ncol = 1
)
```

### Page 8: Eye - hit pos z

```{r, fig.width = 8.3, fig.height = 11.7}
# Arrange Eye Plots - hit pos z
grid.arrange(
  grobs = list(
    arrangeGrob(grobs = eye_plots_z, ncol = 1)
  ), ncol = 1
)
```


### Page 9: Left Disturbance - offset z

```{r, fig.width = 8.3, fig.height = 11}
# Arrange Disturbance Plots - offset z
grid.arrange(
  grobs = list(
    arrangeGrob(grobs = disturbance_plots_z_l, ncol = 1)
  ), ncol = 1
)
```

### Page 10: Left Disturbance - offset x

```{r, fig.width = 8.3, fig.height = 11.7}
# Arrange Disturbance Plots - offset x
grid.arrange(
  grobs = list(
    arrangeGrob(grobs = disturbance_plots_x_l, ncol = 1)
  ), ncol = 1
)
```

### Page 11: Right Disturbance - offset z

```{r, fig.width = 8.3, fig.height = 11.7}
# Arrange Disturbance Plots - offset z
grid.arrange(
  grobs = list(
    arrangeGrob(grobs = disturbance_plots_z_r, ncol = 1)
  ), ncol = 1
)
```

### Page 12: Right Disturbance - offset x

```{r, fig.width = 8.3, fig.height = 11.7}
# Arrange Disturbance Plots - offset x
grid.arrange(
  grobs = list(
    arrangeGrob(grobs = disturbance_plots_x_r, ncol = 1)
  ), ncol = 1
)
```


